\textbf{\sc Deliberative Autonomy for Marine Robotics}

### 2012-01-19 trunk/arch.tex
Added a cal description of  both synchronization and deliberation solvers in the intro of the europa reactor

In T-REX architecture reactors have two core functions;
synchronization where the main focus is to track and refine the
evolution of the state of the world at any single tick, and
deliberation which focus on providing a plan to the agent in order to
complete the reactor {\em Internal} goals. These two processes are
intertwined in the sense that one influences the outcome of the
other.

>>>>

In T-REX architecture reactors have two core functions;
synchronization where the main focus is to track and refine the
evolution of the state of the world at any single tick, and
deliberation which focus on providing a plan to the agent in order to
complete the reactor {\em Internal} goals. These two processes are
intertwined in the sense that one influences the outcome of the
other. They are represented as two europa solvers modifying the same
plan database and for which the execution is managed by the T-REX 
framework rythemed by the time advance during the execuion of the
system:
\begin{enumerate}
\item The synchronization solver is a specialized eurpa solver that
  will integrate in the plan new information about the evolution of
  the External state varaible and ensure that the reactor propagate
  these in order yto both identify its current stetate and inform
  other reactors of any state change on its internal timelines. This
  solver is summoned at the beginnning of every single tick.
\item The deliberation solver is managing the deliberation process of
  the reactor in order to produce a new plan or alter its current plan
  as new goals are given to the reactor or the synchronization solver
  identifying a conflict between the current state of the world and
  the expectations of the previous plan. This process can  span other
  multiple tick and therrfore can be interrupted at any single tick in
  order for the synchronization solver to do its task.
\end{enumerate}
